\section{When constructing this problem set, Jakob ran into some very unfortunate problems.
When he wanted to add a couple of more examples illustrating the power of inductive proofs, the
proofs turned out to be a little bit too powerful. Specifically, Jakob was able to use mathematical
induction to show
1. that all swans have the same colour (presumably white, so that there are no black swans
after all), and
2. that all positive integers are in fact equal.
Both of these claims are fairly disturbing from a mathematical point of view. Please help Jakob
by pointing out clearly what goes wrong in his induction proofs below.}



\subsection{Theorem. All swans have the same colour.
Proof. We prove by induction over n that any set of n swans have the same colour.
For the base case, if we have a set of n 1 swan, then this swan vacuously has the same
colour as itself.
For the induction step, assume as our induction hypothesis that all sets of n swans have
the same colour, and consider a set of n + 1 swans. Fix some swan Sl in this set. If we
remove Sl, then we have n swans left, and by the induction hypothesis they all have the
same colour. Let C be this colour.
Now consider another swan S2 in the set. If we remove S2 from our set of n + 1 swans
instead of Sl, then we again have n swans left, and they all have the same colour by the
induction hypothesis. Since Sl is one of the swans in this set, it must have the same
colour C as all the others. Hence, all n + 1 swans have the same colour.
It follows by the principle of mathematical induction that any set of n swans must always
have the same colour.}

\subsection{Theorem. All positive integers are equal.
Proof. By induction over n.
For the base case, the positive integer 1 is equal to itself.
For the induction step, assume as our induction hypothesis that n — 1 n. Adding 1 to
both sides of this equality, we derive that n n + 1.
It follows from this by the principle of mathematical induction that for all integers n the
equality n n + 1 holds. But then by transitivity we obtain that all integers are equal,
and the claim in the theorem statement has thus been established.}
